\bf\mftitle

### 2011-02-26 doc/jInfer/projecttype/projecttype.tex
#3187361 projecttype doc

With each project created in jInfer is also created specific directory structure on filesystem that describes jInfer project. This structure is described in figure \ref{dir-structure}. Folder in filesystem is considered as jInfer project folder, if contains \emph{jinferproject} subfolder. This folder contains two files, first is \emph{project.properties}, where all properties set for particular project are saved. Second file is \emph{input.files} which is XML file filled with paths to files inserted as input into particular project (structure of this file is described in section \ref{input.files}). \emph{Output} subfolder contains schema files which were generated by jInfer inference.

\section{Structure}

Structure of \jmodule{ProjectType} can be divided into following five main parts.
\begin{itemize}
	\item Base classes - Classes providing main functionality like creation of project, defining operations like move, delete, copy etc. All the base classes are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype} package.
	\item Visualization classes - These classes create tree structure of project in NBP Projects view and are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype.nodes}.
	\item Actions - Classes from \code{cz.cuni.mff.ksi.jinfer.projecttype.actions} package that provides actions allowing adding, removing input files into project, or running the project.
	\item Properties - Classes responsible for creation of project properties window with properties category tree. These are situated in  \code{cz.cuni.mff.ksi.jinfer.projecttype.properties} package.
	\item Project wizard - Classes representing creation of project through new project wizard from  \code{cz.cuni.mff.ksi.jinfer.projecttype.sample} package.
\end{itemize}

@@

\code{JInferProjectFactory} is a factory class implementing \code{ProjectFactory} interface provided by NBP. This class is responsible for loading/saving of jInfer project from/to filesystem and also determining if folder in filesystem is type of jInfer project (contains \emph{jinferproject} subfolder). For this purpose, class has three methods: \code{isProject()}, \code{save()} and \code{load()}. When jInfer project is loaded from filesystem, \code{JInferProjectFactory} creates new instance of \code{JInferProject} passing path to project folder as a constructor parameter. When \code{save()} method is invoced, all the project properties are saved in \emph{projectproperties} file and paths to input files are saved in \emph{input.files}.

@@

Each of the \emph{input} nodes is represented by \code{FolderNode} class and contains \emph{input file} nodes (represented by \code{FileNode} class) representing files added to the jInfer project. Notice that these \emph{input file} nodes represents files from filesystem and are not copied to project folder structure. Because of this, if you delete this nodes from project tree, files from filesystem are not deleted.\\

\code{OutputNode} class represents \emph{Output} node in jInfer project type tree and is slightly different from \emph{input} nodes, because it refers to \emph{output} subfolder in project filesystem hierarchy. In other words, files contained in this folder are shown as subnodes in \emph{Output} node in project tree. This subnodes are represented by \code{OutputFileNode} class. Unlike \emph{input file} nodes, if you delete \emph{output file} node under the \emph{Output} node, file represented by this node is also deleted from filesystem.

@@

To this group of actions belong two actions: action for adding input files into \emph{input folder} node (\code{FileAddAction} class) and action for deleting all input files in \emph{input folder} node (\code{DeleteAllAction} class). \code{FileAddAction} class implements action which opens file choose dialog and selected files are added into particular \emph{file input}node. \code{DeleteAllAction} class simply removes all input files previuosly added into particular \emph{file input} node.

@@

Each jInfer project type has associated properties window through which can user change project-wide properties. This window is accesible through \emph{properties} action in project \emph{root} node context menu. Properties window consists of category tree on a left side and properties pane on a right side. For each category in tree is associated one properties pane. Category in a properties window is represented by NB platform \code{ProjectCustomizer.Category} class and properties pane is represented by \code{JPanel} class. Classes responsible for creation of this properties window are \code{JInferCustomizerProvider} and \code{JInferComponentProvider}.\\

\code{JInferComponentProvider} is very simple class that extends \code{ProjectCustomizer.CategoryComponentProvider} class from NBP and its only method is \code{create()} which takes category as a parameter and returns properties pane. In the \code{JInferCustomizerProvider} class, which extends NBP \code{CustomizerProvider} class, is the core functionality of collecting categories with associated properties panes from all jInfer modules. In section \ref{properties_reg} is described how to create your own category with associated properties pane, which will be present in jInfer project type properties window.\\

\subsubsection{Custom project properties}\label{properties_reg}

>>>>

With each project created in jInfer is also created specific directory structure on file-system that describes jInfer project. This structure is described in figure \ref{dir-structure}. Folder in file-system is considered as jInfer project folder, if contains \emph{jinferproject} sub-folder. This folder contains two files, first is \emph{project.properties}, where all properties set for particular project are saved. Second file is \emph{input.files} which is XML file filled with paths to files inserted as input into particular project (structure of this file is described in section \ref{input.files}). \emph{Output} sub-folder contains schema files which were generated by jInfer inference.

\section{Structure}
PropertiesPanelProvider
Structure of \jmodule{ProjectType} can be divided into following five main parts.
\begin{itemize}
	\item Base classes - Classes providing main functionality like creation of project, defining operations like move, delete, copy etc. All the base classes are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype} package.
	\item Visualization classes - These classes create tree structure of project in NBP Projects view and are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype.nodes}.
	\item Actions - Classes from \code{cz.cuni.mff.ksi.jinfer.projecttype.actions} package that provides actions allowing adding, removing input files into project, or running the project.
	\item Properties - Classes responsible for creation of project properties window with properties category tree. These are situated in  \code{cz.cuni.mff.ksi.jinfer.projecttype.properties} package.
	\item Project wizard - Classes representing creation of project through new project wizard from  \code{cz.cuni.mff.ksi.jinfer.projecttype.sample} package.
\end{itemize}

@@

\code{JInferProjectFactory} is a factory class implementing \code{ProjectFactory} interface provided by NBP. This class is responsible for loading/saving of jInfer project from/to file-system and also determining if folder in file-system is type of jInfer project (contains \emph{jinferproject} sub-folder). For this purpose, class has three methods: \code{isProject()}, \code{save()} and \code{load()}. When jInfer project is loaded from file-system, \code{JInferProjectFactory} creates new instance of \code{JInferProject} passing path to project folder as a constructor parameter. When \code{save()} method is invoked, all the project properties are saved in \emph{projectproperties} file and paths to input files are saved in \emph{input.files}.

@@

Each of the \emph{input} nodes is represented by \code{FolderNode} class and contains \emph{input file} nodes (represented by \code{FileNode} class) representing files added to the jInfer project. Notice that these \emph{input file} nodes represents files from file-system and are not copied to project folder structure. Because of this, if you delete this nodes from project tree, files from file-system are not deleted.\\

\code{OutputNode} class represents \emph{Output} node in jInfer project type tree and is slightly different from \emph{input} nodes, because it refers to \emph{output} sub-folder in project file-system hierarchy. In other words, files contained in this folder are shown as sub-nodes in \emph{Output} node in project tree. This sub-nodes are represented by \code{OutputFileNode} class. Unlike \emph{input file} nodes, if you delete \emph{output file} node under the \emph{Output} node, file represented by this node is also deleted from file-system.

@@

To this group of actions belong two actions: action for adding input files into \emph{input folder} node (\code{FileAddAction} class) and action for deleting all input files in \emph{input folder} node (\code{DeleteAllAction} class). \code{FileAddAction} class implements action which opens file choose dialog and selected files are added into particular \emph{file input}node. \code{DeleteAllAction} class simply removes all input files previously added into particular \emph{file input} node.

@@

Each jInfer project type has associated properties window through which can user change project-wide properties. This window is accessible through \emph{properties} action in context menu of project \emph{root} node. Properties window consists of category tree on a left side and properties pane on a right side. With each category in a tree is associated one properties pane. Structure of the category tree consists of two type of categories: actual category provided by some module and \emph{virtual} category. Actual category has associated properties pane, which is displayed in a right side of the properties window. \emph{Virtual} category displays as a properties pane special information panel that provides information about count and name of modules which are children of this virtual category. Each actual category could have virtual categories as a children or another actual categories, but not both at a same time. On the other side \emph{virtual} category can have only actual categories as a children. If a \emph{virtual} category has no child, this category is not displayed in a category tree.\\

Category in a properties window is represented by NB platform \code{ProjectCustomizer.Category} class and properties pane is represented by \code{JPanel} class. Classes responsible for creation of this properties window are\\ \code{JInferCustomizerProvider} and \code{JInferComponentProvider}. From Jinfer module point of view is properties category represented by \code{PropertiesPanelProvider} interface and associated properties pane by \code{AbstractPropertiesPanel} abstract class. How to use this interface and abstract class to create custom project properties category presented in jInfer project type properties windowis described in section \ref{properties_reg}.\\

\code{JInferComponentProvider} is very simple class that extends \code{ProjectCustomizer.CategoryComponentProvider} class from NBP and its only method is \code{create()} which takes category as a parameter and returns properties pane. In the \code{JInferCustomizerProvider} class, which extends NBP \code{CustomizerProvider} class, is the core functionality of collecting categories (\code{PropertiesPanelProvider} interface) with associated properties panes (\code{AbstractPropertiesPanel} class) from all jInfer modules.\\

\subsubsection{Custom project properties category}\label{properties_reg}

As was written before, each jInfer project properties category is represented in jInfer modules by \code{PropertiesPanelProvider} interface. To create new category, this interface must be implemented and implementation must be annotated by the following code.
\begin{verbatim}
	@ServiceProvider(service = PropertiesPanelProvider.class)
\end{verbatim}

\code{PropertiesPanelProvider} interface provides the following methods:
\begin{itemize}
	\item getName() - Gets a programmatic name of category
	\item getDisplayName() - Gets a name of category displayed in properties window.
	\item getPriority() - Gets a priority of category, by which is sorted among other sibling categories in a tree.
	\item getPanel() - Gets \code{AbstractPropertiesPanel} representing the category properties pane.
	\item getSubCategories() - Gets a \code{List} of \code{VirtualCategoryPanel} representing virtual category child.
\end{itemize}

\begin{figure}
	\centering\includegraphics[scale=\myscale]{uml_properties}
	\caption{Project directory structure} \label{uml-properties}
\end{figure}
